### 2020-09-03 text/manuscript.tex
Include .bbl in .tex

%\begin{thebibliography}{10}

%\end{thebibliography}

\bibliography{socdist}

>>>>

\begin{thebibliography}{10}

\bibitem{Bootsma2007-ww}
Bootsma MCJ, Ferguson NM.
\newblock The effect of public health measures on the 1918 influenza pandemic
  in {US} cities.
\newblock Proc Natl Acad Sci. 2007;.

\bibitem{Markel2007-ad}
Markel H, Lipman HB, Navarro JA, Sloan A, Michalsen JR, Stern AM, et~al.
\newblock Nonpharmaceutical interventions implemented by {US} cities during the
  1918-1919 influenza pandemic.
\newblock JAMA. 2007;298(6):644--654.

\bibitem{Hatchett2007-gc}
Hatchett RJ, Mecher CE, Lipsitch M.
\newblock Public health interventions and epidemic intensity during the 1918
  influenza pandemic.
\newblock Proc Natl Acad Sci. 2007;104(18):7582--7587.

\bibitem{Wilder-Smith2020-jj}
Wilder-Smith A, Freedman DO.
\newblock Isolation, quarantine, social distancing and community containment:
  pivotal role for old-style public health measures in the novel coronavirus
  ({2019-nCoV}) outbreak.
\newblock J Travel Med. 2020;27(2).

\bibitem{Anderson2020-qk}
Anderson RM, Heesterbeek H, Klinkenberg D, Hollingsworth TD.
\newblock How will country-based mitigation measures influence the course of
  the {COVID-19} epidemic?
\newblock Lancet. 2020;.

\bibitem{Cohen2020-jw}
Cohen J, Kupferschmidt K.
\newblock Mass testing, school closings, lockdowns: Countries pick tactics in
  `war' against coronavirus.
\newblock Science. 2020;.

\bibitem{Thompson2020-lc}
Thompson SA, Serkez Y.
\newblock How Has Your State Reacted to Social Distancing?
\newblock The New York Times. 2020;.

\bibitem{noauthor_2020-xi}
Mayor de Blasio Issues New Guidance to New Yorkers; 2020.
\newblock
  \url{https://www1.nyc.gov/office-of-the-mayor/news/173-20/mayor-de-blasio-issues-new-guidance-new-yorkers}.

\bibitem{Adda2016-mn}
Adda J.
\newblock Economic Activity and the Spread of Viral Diseases: Evidence from
  High Frequency Data.
\newblock Q J Econ. 2016;131(2):891--941.

\bibitem{Wren-Lewis2020-vc}
Wren-Lewis S.
\newblock The economic effects of a pandemic.
\newblock In: Baldwin R, Weder~di Mauro B, editors. Economics in the Time of
  {COVID-19}. London, UK: CEPR Press; 2020. p. 109--112.

\bibitem{Henderson2010-mv}
Henderson JV.
\newblock Cities and Development.
\newblock J Reg Sci. 2010;50(1):515--540.

\bibitem{Henderson2002-ji}
Henderson V.
\newblock Urbanization in Developing Countries.
\newblock World Bank Res Obs. 2002;17(1):89--112.

\bibitem{Herrendorf2014-jx}
Herrendorf B, Rogerson R, Valentinyi {\'A}.
\newblock Growth and Structural Transformation.
\newblock In: Aghion P, Durlauf SN, editors. Handbook of Economic Growth.
  vol.~2. Elsevier; 2014. p. 855--941.

\bibitem{Duarte2019-kc}
Duarte M, Restuccia D.
\newblock Relative Prices and Sectoral Productivity.
\newblock J Eur Econ Assoc. 2019;.

\bibitem{Dingel2020-lh}
Dingel J, Neiman B.
\newblock How Many Jobs Can be Done at Home?
\newblock Becker Friedman Institute, University of Chicago; 2020.

\bibitem{von2020labour}
Von~Gaudecker HM, Holler R, Janys L, Siflinger B, Zimpelmann C.
\newblock Labour supply in the early stages of the CoViD-19 Pandemic: Empirical
  Evidence on hours, home office, and expectations. 2020;.

\bibitem{Charlot2004-zr}
Charlot S, Duranton G.
\newblock Communication externalities in cities.
\newblock J Urban Econ. 2004;56(3):581--613.

\bibitem{Tian2019-wq}
Tian L.
\newblock Division of Labor and Productivity Advantage of Cities: Theory and
  Evidence from Brazil; 2019.

\bibitem{National_Center_for_ONET_Development2020-wj}
{National Center for O*NET Development}. {O*NET} {OnLine} [dataset]; 2020.

\bibitem{CBP}
{U S  Bureau of the Census}. County Business Patterns [dataset]; 2017.

\bibitem{SafeGraph2020-gn}
{SafeGraph}. Patterns [dataset]; 2020.

\bibitem{ATUS}
{U S  Bureau of Labor Statistics}. American Time Use Survey [dataset]; 2018.

\bibitem{Smith1778-qq}
Smith A.
\newblock An Inquiry into the Nature and Causes of the Wealth of Nations (Book
  I).
\newblock London: W. Strahan; T. Cadell; 1778.

\bibitem{Becker1992-ac}
Becker GS, Murphy KM.
\newblock The Division of Labor, Coordination Costs, and Knowledge.
\newblock Q J Econ. 1992;107(4):1137--1160.

\bibitem{Marshall1920-ps}
Marshall A.
\newblock Principles of Economics (eighth edition).
\newblock London: MacMillan; 1920.

\bibitem{Krugman1991-gr}
Krugman P.
\newblock Geography and Trade.
\newblock Cambridge: MIT Press; 1991.

\bibitem{Garicano2009-jv}
Garicano L, Hubbard TN.
\newblock Specialization, Firms, and Markets: The Division of Labor within and
  between Law Firms.
\newblock J Law Econ Organ. 2009;25(2):339--371.

\bibitem{Firpo2011-hp}
Firpo S, Fortin NM, Lemieux T.
\newblock Occupational Tasks and Changes in the Wage Structure.
\newblock IZA; 2011. 5542.

\bibitem{Autor2013-sh}
Autor DH, Dorn D.
\newblock The Growth of {Low-Skill} Service Jobs and the Polarization of the
  {US} Labor Market.
\newblock Am Econ Rev. 2013;103(5):1553--1597.

\bibitem{Jin2020-tq}
Jin B, McGill A. Who is most at risk in the coronavirus crisis: 24 million of
  the lowest-income workers; 2020.
\newblock
  \url{https://www.politico.com/interactives/2020/coronavirus-impact-on-low-income-jobs-by-occupation-chart/}.

\bibitem{Leibovici2020-qr}
Leibovici F, Santacreu AM, Famiglietti M. Social Distancing and
  {Contact-Intensive} Occupations; 2020.
\newblock
  \url{https://www.stlouisfed.org/on-the-economy/2020/march/social-distancing-contact-intensive-occupations}.

\bibitem{Mongey2020-qc}
Mongey S, Weinberg A.
\newblock Characteristics of workers in low work-from-home and high
  personal-proximity occupations; 2020.

\bibitem{CES}
{U S  Bureau of Labor Statistics}. Current Employment Statistics [dataset];
  2020.

\bibitem{employment-matrix}
{U S  Bureau of Labor Statistics}. National Employment Matrix [dataset]; 2020.

\bibitem{Caliendo2014-mr}
Caliendo L, Parro F, Rossi-Hansberg E, Sarte PD.
\newblock The Impact of Regional and Sectoral Productivity Changes on the
  {U.S}. Economy.
\newblock National Bureau of Economic Research, Inc; 2014. 20168.

\bibitem{Caselli2020-nf}
Caselli F, Koren M, Lisicky M, Tenreyro S.
\newblock Diversification Through Trade.
\newblock Q J Econ. 2020;135(1):449--502.

\bibitem{Baldwin2020-wb}
Baldwin R, Tomiura E.
\newblock Thinking ahead about the trade impact of {COVID-19}.
\newblock In: Baldwin R, Weder~di Mauro B, editors. Economics in the Time of
  {COVID-19}. London, UK: CEPR Press; 2020. p. 59--61.

\bibitem{Barrot2020-jf}
Barrot JN, Grassi B, Sauvagnat J.
\newblock Sectoral effects of social distancing; 2020.

\bibitem{Gaspar1998-gy}
Gaspar J, Glaeser E.
\newblock Information Technology and the Future of Cities.
\newblock J Urban Econ. 1998;43(1):136--156.

\bibitem{Storper2004-mg}
Storper M, Venables AJ.
\newblock Buzz: face-to-face contact and the urban economy.
\newblock J Econ Geogr. 2004;4(4):351--370.

\bibitem{Cuberes2013-js}
Cuberes D.
\newblock Are Internet and {Face-to-Face} Contacts Complements or Substitutes?
  Evidence from Internet Traffic between Cities; 2013. 2013010.

\bibitem{Glaeser2002-mw}
Glaeser EL, Shapiro JM.
\newblock Cities and Warfare: The Impact of Terrorism on Urban Form.
\newblock J Urban Econ. 2002;51(2):205--224.

\bibitem{Harrigan2002-ik}
Harrigan J, Martin P.
\newblock Terrorism and the Resilience of Cities.
\newblock Economic Policy Review. 2002;8(2).

\end{thebibliography}
